Paper_Figure

### 2024-01-08 Demo_marrow_facs.Rmd
simple demo
24/01/08

@@

```{r}
# Obtain diffusion KL score
score_result = fast_calculate_multi_score(W = W, init_state = rho, P_ls = P_ls)

>>>>

```{r}
# # save to hdf5 file
# df = sub.srat@meta.data[,c("design_coarse","celltype1205")]
# # BiocManager::install("rhdf5")
# library(rhdf5)
# h5write(dat, 'Bone_marrow_facs_mtx.h5', 'dataset')
# fwrite(df,file = "HL234_meta.txt",row.names = TRUE)
```

@@

```{r}
# Obtain diffusion KL score
score_result = fast_get_lmds(W = W, init_state = rho, P_ls = P_ls)

### 2024-01-08 Marker_identfication_benchmark.Rmd
24/01/08

if(tissue_fullname == "Bone marrow"){
  tissue_name = "marrow_facs"
  if (!file.exists('facs_Marrow_seurat_tiss.Robj')) {
   # If load url doesn't work, please download it and load from your working directory
  options(timeout=6000)
  download.file("https://figshare.com/ndownloader/files/13092380",
                destfile = 'facs_Marrow_seurat_tiss.Robj', method = 'libcurl')
  }
  load('facs_Marrow_seurat_tiss.Robj')
  tiss <- UpdateSeuratObject(tiss)
}if(tissue_fullname == "Pancreas"){
  tissue_name = "pancreas_facs"
  if (!file.exists('facs_Pancreas_seurat_tiss.Robj')) {
     # If load url doesn't work, please download it and load from your working directory
    options(timeout=6000)
    download.file("https://figshare.com/ndownloader/files/13092386",
                  destfile = 'facs_Pancreas_seurat_tiss.Robj', method = 'libcurl')
  }
  load('facs_Pancreas_seurat_tiss.Robj')
  tiss <- UpdateSeuratObject(tiss)
}if(tissue_fullname == "Lung"){
  tissue_name = "lung_facs"
  if (!file.exists('facs_Lung_seurat_tiss.Robj')) {
     # If load url doesn't work, please download it and load from your working directory
    options(timeout=6000)
    download.file("https://figshare.com/ndownloader/files/13092194",
                  destfile = 'facs_Lung_seurat_tiss.Robj', method = 'libcurl')
   }
  load('facs_Lung_seurat_tiss.Robj')
  tiss <- UpdateSeuratObject(tiss)
}if(tissue_fullname == "Thymic"){
  options(timeout=6000)
  if (!file.exists('Human_Thymic_Epithelial_seurat_tiss.Robj')) {
     # If load url doesn't work, please download it and load from your working directory
    options(timeout=6000)
    download.file("https://datasets.cellxgene.cziscience.com/046d2e35-2ee6-4159-8db7-7b1039fe0005.rds",
                  destfile = 'Human_Thymic_Epithelial_seurat_tiss.Robj', method = 'libcurl')
  }
  tiss <- readRDS()
}

@@

score_measure =do.call(rbind,lapply(c(method_ls,"All genes"),function(method){
  if(method == "All genes"){
    top_gs = rownames(df_benchmark)
    top_n = length(top_gs)
  }else{
    top_gs = rownames(df_benchmark)[order(df_benchmark[,method])]
    top_n = c(seq(50,90,10),seq(100,900,100),seq(1000,3000,500),seq(4000,9000,1000),seq(10000,max(df_benchmark),2000))
  }
  result = unlist(lapply(top_n, function(top){
    tiss <- RunPCA(tiss, features = top_gs[1:top], npcs = 20)
    d = dist(Embeddings(tiss, reduction = "pca"))
    c = as.integer(factor(tiss$cell_ontology_class[labels(d)]))

    # # Silhouette score
    # s1 = mean(as.data.frame(cluster::silhouette(c, d)[,]) %>%
    #   group_by(cluster) %>%
    #   summarize(mean_silhouette = mean(sil_width)) %>%.$mean_silhouette)

    # Density-index
    nn.dist = FNN::get.knn(Embeddings(tiss, reduction = "pca"), k = 10, algorithm = "kd_tree")$nn.dist
    sdVec <- stats::na.omit(tiss@reductions$pca@stdev)
    length_scale <- sqrt(sum(sdVec^2))
    s2 = length_scale/mean(nn.dist)

@@

write.table(score_measure,file = file.path(folder_path, paste0(tissue_name,"_density_index.csv")),row.names = FALSE)
```

>>>>

if(tissue_fullname == "Bone marrow"){
  tissue_name = "marrow_facs"
  if (!file.exists('facs_Marrow_seurat_tiss.Robj')) {
   # If load url doesn't work, please download it and load from your working directory
  options(timeout=6000)
  download.file("https://figshare.com/ndownloader/files/13092380",
                destfile = 'facs_Marrow_seurat_tiss.Robj', method = 'libcurl')
  }
  load('facs_Marrow_seurat_tiss.Robj')
  tiss <- UpdateSeuratObject(tiss)
}if(tissue_fullname == "Pancreas"){
  tissue_name = "pancreas_facs"
  if (!file.exists('facs_Pancreas_seurat_tiss.Robj')) {
     # If load url doesn't work, please download it and load from your working directory
    options(timeout=6000)
    download.file("https://figshare.com/ndownloader/files/13092386",
                  destfile = 'facs_Pancreas_seurat_tiss.Robj', method = 'libcurl')
  }
  load('facs_Pancreas_seurat_tiss.Robj')
  tiss <- UpdateSeuratObject(tiss)
}if(tissue_fullname == "Lung"){
  tissue_name = "lung_facs"
  if (!file.exists('facs_Lung_seurat_tiss.Robj')) {
     # If load url doesn't work, please download it and load from your working directory
    options(timeout=6000)
    download.file("https://figshare.com/ndownloader/files/13092194",
                  destfile = 'facs_Lung_seurat_tiss.Robj', method = 'libcurl')
   }
  load('facs_Lung_seurat_tiss.Robj')
  tiss <- UpdateSeuratObject(tiss)
}if(tissue_fullname == "Thymic"){
  options(timeout=6000)
  if (!file.exists('Human_Thymic_Epithelial_seurat_tiss.Robj')) {
     # If load url doesn't work, please download it and load from your working directory
    options(timeout=6000)
    download.file("https://datasets.cellxgene.cziscience.com/046d2e35-2ee6-4159-8db7-7b1039fe0005.rds",
                  destfile = 'Human_Thymic_Epithelial_seurat_tiss.Robj', method = 'libcurl')
  }
}

@@

score_measure =do.call(rbind,lapply(c(method_ls,"All genes"),function(method){
  if(method == "All genes"){
    top_gs = rownames(df_benchmark)
    top_n = length(top_gs)
  }else{
    top_gs = rownames(df_benchmark)[order(df_benchmark[,method])]
    top_n = c(seq(50,90,10),seq(100,900,100),seq(1000,3000,500),seq(4000,9000,1000),seq(10000,max(df_benchmark),2000))
  }
  result = unlist(lapply(top_n, function(top){
    features = top_gs[1:top]
    tiss <- tiss %>% ScaleData(features = features) %>% RunPCA(features = features, npcs = 20)
    # # Silhouette score
    # d = dist(Embeddings(tiss, reduction = "pca"))
    # c = as.integer(factor(tiss$cell_ontology_class[labels(d)]))
    # s1 = mean(as.data.frame(cluster::silhouette(c, d)[,]) %>%
    #   group_by(cluster) %>%
    #   summarize(mean_silhouette = mean(sil_width)) %>%.$mean_silhouette)

    # Density-index
    nn.dist = FNN::get.knn(Embeddings(tiss, reduction = "pca"), k = 10, algorithm = "kd_tree")$nn.dist
    sdVec <- stats::na.omit(tiss@reductions$pca@stdev)
    length_scale <- sqrt(sum(sdVec^2)) # length-scale * sqrt(2*(N-1)/N) = d_rms
    s2 = length_scale/mean(nn.dist)

@@

# error bar & null distribution
null_score_measure = do.call(rbind,lapply(top_n,function(top){
  set.seed(top)
  seed_ls = sample(1:1e5,size = 100)
  random_top_gs = lapply(seed_ls,function(sed){
    set.seed(sed)
    sample(rownames(df_benchmark),top,replace = FALSE)
  })
  result = unlist(lapply(random_top_gs, function(g_ls){
    features = g_ls
    tiss <- tiss %>% ScaleData(features = features) %>% RunPCA(features = features, npcs = 20)
    # Density-index
    nn.dist = FNN::get.knn(Embeddings(tiss, reduction = "pca"), k = 10, algorithm = "kd_tree")$nn.dist
    sdVec <- stats::na.omit(tiss@reductions$pca@stdev)
    length_scale <- sqrt(sum(sdVec^2))
    s2 = length_scale/mean(nn.dist)
    s2
  }))
  result = data.frame(TopGene = top,DensityIndex = result)
}) )

write.table(null_score_measure,file = file.path(folder_path, paste0(tissue_name,"_DI_null.csv")),row.names = FALSE)
write.table(score_measure,file = file.path(folder_path, paste0(tissue_name,"_density_index.csv")),row.names = FALSE)
```

### 2024-01-08 paper_figure.Rmd
24/01/08

P_ls = Obtain_Pls(W = W, max_time = 2^15)
rho = Rowwise_normalize(dat[,colnames(W)])
res = fast_calculate_multi_score(W = W, init_state = rho, P_ls = P_ls)
```
```{r}
# Plot knn graph
p = plot_knn_graph(affinity_m = W, layout = visual_space)
ggsave(filename = "fig-pipeline1.png", plot = p, width = 6, height = 5, dpi = 300)
```
```{r}
# Check Diffusion KL pattern for several genes
# good gene: Igll1,Fcnb # garbage marker: Fkbp1b, Tnks1bp1, Magi2,Uchl4
genes = c("Igll1","Tnks1bp1") 
# genes_label = c("localized","non_localized")
check_time = c(0,2^3,2^10,2^15)
p = Visualize_score_pattern(res, genes = genes, add_point = check_time)

@@

>>>>

P_ls = Obtain_Pls(W = W, max_time = 2^15)
rho = Rowwise_normalize(dat[,colnames(W)])
res = fast_get_lmds(W = W, init_state = rho, P_ls = P_ls)
```
```{r}
# Plot knn graph
p = plot_knn_graph(affinity_m = W, layout = visual_space)
ggsave(filename = "fig-pipeline1.png", plot = p, width = 6, height = 5, dpi = 300)
```
```{r}
# Check Diffusion KL pattern for several genes
# good gene: Igll1,Fcnb # garbage marker: Fkbp1b, Tnks1bp1, Magi2,Uchl4
genes = c("Igll1","Tnks1bp1") 
# genes_label = c("localized","non_localized")
check_time = c(0,2^3,2^10,2^15)
p = Visualize_score_pattern(res, genes = genes, add_point = check_time)

@@

# # Add null distribution
# null_score_measure = read.csv(paste0(path,tissue_name,"_DI_null.csv"),header = TRUE)
# fig = fig + geom_boxplot(data = null_score_measure, aes(x = TopGene, y = DensityIndex, group = TopGene), inherit.aes = FALSE)
